Fast Fashion's Rapid Rate of Overoduction is Observedly Unsustainable, & Unethical: Why and How did we get here?

### 2023-04-02 outputs/paper.qmd
Editing title

---
title: "Fast Fashion's Production Rate is Observedly Unsustainable: Why and How did we get here?"
author: "Jayden Jung"
thanks: "Code and data are available at: https://github.com/jj-andj/fast-fashion-analysis"
date: "April 21, 2023"
date-format: long
format: 
  pdf: 
    documentclass: article
    geometry: margin = 1in
    abstract: "An abstract is included and appropriately pitched to a non-specialist audience. The abstract answers: 1) what was done, 2) what was found, and 3) why this matters (all at a high level). Likely four sentences. Abstract must make clear what we learn about the world because of this paper."
output: 
  bookdown::pdf_document2
toc: false
fig_caption: yes
nocite: '@*'
bibliography: references.bib
---

>>>>

---
title: "Fast Fashion's Rapid Rate of Overoduction is Observedly Unsustainable, & Unethical: Why and How did we get here?"
author: "Jayden Jung"
thanks: "Code and data are available at: https://github.com/jj-andj/fast-fashion-analysis"
date: "April 21, 2023"
date-format: long
format: 
  pdf: 
    documentclass: article
    geometry: margin = 1in
    abstract: "An abstract is included and appropriately pitched to a non-specialist audience. The abstract answers: 1) what was done, 2) what was found, and 3) why this matters (all at a high level). Likely four sentences. Abstract must make clear what we learn about the world because of this paper."
output: 
  bookdown::pdf_document2
toc: false
fig_caption: yes
nocite: '@*'
bibliography: references.bib
---
